Manuscript 1 code

### 2024-10-02 manuscript_1_code.Rmd
Completed figure 4 with functional richness

#each quad only has ONE value, averaged through time 
#1200 quads in this data set
#this is used in figure 4 things
```

@@

@@

## Figure 4 Full Plot
```{r ggpubr fig4}
fig4_plot_list <- list(figure_4a, figure_4c, figure_4d, figure_4f)
figure_4 <- ggarrange(plotlist = fig4_plot_list, 
                      ncol = 2, nrow = 2, 
                      labels = c("a.", "b."),
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 20, color = "black", face = "plain"))

#ggsave(filename = "output/figure_4.png", figure_4, height = 10, width = 20)
```

>>>>

#each quad only has ONE value, averaged through time 
#1200 quads in this data set
#this is used in figure 4 things

#merge with fg data 
fg_stability_quad_level <- merge(fg_summary_wide_meta_through_time, diversity_stability_synchrony, 
                              by = 
                                c("location","site", "habitat"))

dss_ranges_fg <- fg_stability_quad_level %>%
  group_by(habitat) %>%
  summarise(min_richness_fg = min(fg_richness_mean),
            max_richness_fg = max(fg_richness_mean),
            min_stability= min(cover_stability, na.rm = TRUE),
            max_stability = max(cover_stability, na.rm = TRUE))
```

### figure 4b model
```{r fig4b fg richness stability mod}

rich_stab_mod_fg <- glmmTMB(cover_stability ~ fg_richness_mean*habitat + (1|site), family = Gamma(link = "log"), data = fg_stability_quad_level)

summary(rich_stab_mod_fg)
car::Anova(rich_stab_mod_fg)

#                             Chisq Df Pr(>Chisq)    
# fg_richness_mean         3079.229  1  < 2.2e-16 ***
# habitat                   118.605  3  < 2.2e-16 ***
# fg_richness_mean:habitat   25.692  3  1.107e-05 ***

hist(residuals(rich_stab_mod_fg)) # looks fine
plot(residuals(rich_stab_mod_fg) ~ fitted(rich_stab_mod_fg)) # same as usual 
r.squaredGLMM(rich_stab_mod_fg) # 0.819, 0.828
emtrends(rich_stab_mod_fg, pairwise ~ habitat, var = "fg_richness_mean") 
#  fringing different from all others

```
```{r figure 4b plot setup}
rich_stab_emm_fg <- emmip(rich_stab_mod_fg,
                        habitat ~ fg_richness_mean,
                        at = list(fg_richness_mean = seq(0,10,0.01)), plotit = F, CIs = T)

filtered_rich_stab_effects_fg <- rich_stab_emm_fg %>%
  left_join(dss_ranges_fg, by = c("habitat")) %>%
  filter(fg_richness_mean >= min_richness_fg & fg_richness_mean <= max_richness_fg)
```

### plot fig 4b

```{r plot figure 4b}
(figure_4b <- 
  ggplot() +
  geom_point(data = fg_stability_quad_level,
             aes(x = fg_richness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects_fg, aes(x = fg_richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects_fg, aes(x = fg_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "4b.") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

#ggsave(filename = "output/figure_4b_v2.png", figure_4b, height = 10, width = 14)
```

@@

## figure 4e

### setup and model

```{r functional group -- stability site}

#need to get average functional richness through time! 
fg_summary_site_wide_summary <- fg_summary_site_wide %>%
  group_by(habitat, site) %>%
  summarize(avg_richness_fg = mean(fg_richness_site),
            se_richness_fg = sd(fg_richness_site)/sqrt(n()))

#n = 24!

# merge
stability_site_level_fg <- merge(diversity_stability_synchrony_site, fg_summary_site_wide_summary, by = c("site", "habitat"))

# extract relevant ranges for plotting
dss_ranges_site_fg_stab <- stability_site_level_fg %>%
  group_by(habitat) %>%
  summarise(min_richness_fg = min(avg_richness_fg),
            max_richness_fg = max(avg_richness_fg),
            min_stability= min(cover_stability),
            max_stability = max(cover_stability))

rich_stab_mod_site_fg <- glmmTMB(cover_stability~ avg_richness_fg*habitat, family = Gamma(link = "log"), data = stability_site_level_fg)
summary(rich_stab_mod_site_fg)
Anova(rich_stab_mod_site_fg)

#                           Chisq Df Pr(>Chisq)   
# avg_richness_fg          3.4019  1   0.065122 . 
# habitat                 12.8194  3   0.005044 **
# avg_richness_fg:habitat  7.9921  3   0.046176 *

hist(residuals(rich_stab_mod_site_fg)) # blocky but fine
plot(residuals(rich_stab_mod_site_fg) ~ fitted(rich_stab_mod_site_fg)) # heteroskedastic
r.squaredGLMM(rich_stab_mod_site_fg) # 0.563
emtrends(rich_stab_mod_site_fg, pairwise ~ habitat, var = "avg_richness_fg") 
# Fringing different from outer 10

```{r figure 4e setup}
rich_stab_emm_site_fg <- emmip(rich_stab_mod_site_fg,
                        habitat ~ avg_richness_fg,
                        at = list(avg_richness_fg = seq(0,10,0.01)), plotit = F, CIs = T)

filtered_rich_stab_effects_site <- rich_stab_emm_site_fg %>%
  left_join(dss_ranges_site_fg_stab, by = c("habitat")) %>%
  filter((avg_richness_fg >= min_richness_fg) & (avg_richness_fg <= max_richness_fg))

### plot figure 4e

```{r figure 4e}
(figure_4e <- 
  ggplot() +
  geom_point(data = stability_site_level_fg,
             aes(x = avg_richness_fg, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects_site, aes(x = avg_richness_fg, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects_site, aes(x = avg_richness_fg, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "Functional Richness", title = "4e.") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

#ggsave(filename = "output/figure_4e_v2.png", figure_4e, height = 10, width = 14)
```

@@

## Figure 4 Full Plot
```{r ggpubr fig4, fig.height = 8, fig.width=16}

(figure_4 <- ggarrange(figure_4a, figure_4b, figure_4c, figure_4d, figure_4e, figure_4f, 
                      ncol = 3, nrow = 2, 
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 20, color = "black", face = "plain")))

# ggsave(filename = "output/figure_4.png", figure_4, height = 8, width = 16)
```
